---
title: "Initial Korean covid 19"
author: "Mya Orozco Rodriguez"
date: "9/26/2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  



  



```{r}
barchartGC(~result + Sex,data=kRdata )
barchartGC(~result + Sex,data=kRdata , type="percent")

```
 
  The majority of female who were alive was about 55%, while 45% were male.But out of the population that died, nearly 65% were male while 45% were female. This basically just means there was significant difference between the amounts of males that died than females.
  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

From the data we can see that the majority of the alive population was female with the ratio of 56:44. however of the dead population the majority were males with the ratio of 36:64. 3% of the male population were dead while 1.4% of the female population were dead showing that the male population which more than double than the female population of dead people.

## Inferential results 




## Conclusions

